\begin{abstract}

本文旨在探索超音速牛奶喷射与时间旅行的概率动力学这一领域的研究。通过系统的理论分析和数值模拟，本文深入研究了这一课题的核心动力学特性。研究首先建立了超音速牛奶喷射的流体动力学模型，分析了高速喷射过程中的流场分布、速度分布和喷射效率。在此基础上，引入概率动力学方法，探讨了时间旅行的理论框架和实现可能性。通过耦合超音速喷射与时间旅行模型，揭示了二者之间的相互作用机制和概率分布规律。

研究结果表明，超音速牛奶喷射的流场特性与时间旅行的概率分布存在显著耦合关系。通过优化喷射参数，可以有效提高时间旅行的概率密度。本研究为超音速喷射和时间旅行领域的理论发展提供了新的视角和方法。

\keywords{超音速牛奶喷射，时间旅行，概率动力学，流体动力学，数值模拟}

\end{abstract}



\begin{englishabstract}

This thesis aims to explore the field of probabilistic dynamics of supersonic milk jetting and time travel. Through systematic theoretical analysis and numerical simulation, this study investigates the core dynamic characteristics of this subject. The research first establishes a hydrodynamic model of supersonic milk jetting, analyzing flow field distribution, velocity distribution, and jetting efficiency during high-speed jetting processes. Based on this foundation, probabilistic dynamics methods are introduced to explore the theoretical framework and implementation possibilities of time travel. By coupling supersonic jetting and time travel models, the interaction mechanisms and probability distribution patterns between the two are revealed.

The results indicate a significant coupling relationship between the flow characteristics of supersonic milk jetting and the probability distribution of time travel. By optimizing jetting parameters, the probability density of time travel can be effectively improved. This research provides new perspectives and methods for the theoretical development of supersonic jetting and time travel.

\englishkeywords{supersonic milk jetting; time travel; probabilistic dynamics; fluid dynamics; numerical simulation}

\end{englishabstract}
